Computing Entropies With Nested Sampling

### 2017-03-15 paper/ms.tex
Included final results on sinusoid problem

The results for the uneven observing schedule were:
\begin{align}
H'_{\tau}     &= 1.122 \pm 0.028 \\
H'_{\d}       &= 895.5 \pm 1.5   \\
H'_{\tau, \d} &= 874.7 \pm 1.5    \\
I_{\tau, \d} &= 30.13 \pm 0.70
\end{align}

The difference in mutual informations between the two observation
schedules is $2.3 \pm 1.3$ nats, suggesting a slight advantage to the
uneven observing schedule, in terms of the data's relevance to inference
of the log-period of the signal.
In a serious experimental design situation, the relevance is not the only
consideration (or the answer to every experimental design problem would
be to obtain more data without limit), but it is a very important one.

@@

The computational resources needed to compute these quantities was quite large
--- three lots of 1,000 repetitions of Nested Sampling, in all
(though the algorithm can be parallelised trivially).
However, it is worth reflecting on the complexity of the calculation that
has been done.

@@

\subsection{Multimodality and precisional questions}

When inferring the period of an oscillating signal, multimodal posterior
distributions for the period are common \citep{gregoryTrimodal, exoplanet}

The multimodality of the posterior here raises an interesting issue. Is
the question we really want answered ``what is the value of $T$
{\bf precisely}?'', to which the mutual information relates?
Most practicing scientists would not feel particularly informed to learn
that the vast majority of possibilities had been ruled out, if the
posterior still consisted of several widely separated modes!
Perhaps, in some applications, a more appropriate question is
``what is the value of $T$ to within $\pm$ 10\%''
{\todo or something like that.}
{\query The multimodality of the posterior in this problem (sometimes) might
affect mixing sufficiently that the NS gets the incorrect answer. Be
careful! And maybe use an example where this is unlikely, or double
check it using brute force.}

>>>>

The results for the uneven observing schedule, again in terms of log
probabilities, are:
\begin{align}
H_{\tau}     &= 6.243  \pm 0.024 \\
H_{\d}       &= 712.77 \pm 0.35   \\
H_{\tau, \d} &= 715.84 \pm 0.35    \\
I_{\tau, \d} &= 5.21 \pm 0.40
\end{align}

The difference in mutual informations between the two observation
schedules, assuming a uniform prior on this difference,
is just $0.25 \pm 0.55$ nats, suggesting (extremely weakly)
a slight advantage to the
uneven observing schedule, in terms of the data's relevance to inference
of the log-period of the signal. The situation may be different if we
had allowed for shorter periods to be possible, as irregular observing
schedules are known to reduce aliasing and ambiguity in the inferred period.
When inferring the period of an oscillating signal, multimodal posterior
distributions for the period are common \citep{gregoryTrimodal, exoplanet}.
The multimodality of the posterior here raises an interesting issue. Is
the question we really want answered ``what is the value of $T$
{\bf precisely}?'', to which the mutual information relates?
Most practicing scientists would not feel particularly informed to learn
that the vast majority of possibilities had been ruled out, if the
posterior still consisted of several widely separated modes!
Perhaps, in some applications, a more appropriate question is
``what is the value of $T$ to within $\pm$ 10\%'', or something along these
lines.

In a serious experimental design situation, the relevance is not the only
consideration (or the answer to every experimental design problem would
be to obtain more data without limit), but it is a very important one.

@@

The computational resources needed to compute these quantities was quite large,
as Nested Sampling appears in the inner loop of the algorithm.
However, it is worth reflecting on the complexity of the calculation that
has been done.

@@
